# Experiment 2 {#alignment-3-appendix}

## Instructions {#instructions-materials-alignment-3-appendix}

Figure \@ref(fig:instructions-materials-alignment-3) shows the instructions.

(ref:instructions-materials-alignment-3) Experiment 2 instructions.

```{r instructions-materials-alignment-3, fig.cap = "(ref:instructions-materials-alignment-3)"}
file.path(
  materials_3,
  "instructions.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

## NPV Test {#npv-test-materials-alignment-3}

Participants were given more extensive information about NPV than in the
previous experiment and were tested on their ability to calculate simple
averages from given numerical ranges, as shown in
Figures \@ref(fig:npv-test-1-materials-alignment-3)
and \@ref(fig:npv-test-2-materials-alignment-3).

(ref:npv-test-1-materials-alignment-3) Experiment 2 NPV test.

```{r npv-test-1-materials-alignment-3, fig.cap = "(ref:npv-test-1-materials-alignment-3)", out.width = "90%"}
npv_test_1 <- file.path(
  materials_3,
  "npv_test_1.png"
) %>%
  image_read()

npv_test_2 <- file.path(
  materials_3,
  "npv_test_2.png"
) %>%
  image_read()

c(
  npv_test_1,
  npv_test_2
) %>%
  image_trim() %>%
  image_append(stack = TRUE) %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:npv-test-2-materials-alignment-3) Experiment 2 NPV test answers.

```{r npv-test-2-materials-alignment-3, fig.cap = "(ref:npv-test-2-materials-alignment-3)", out.width = "60%"}
file.path(
  materials_3,
  "npv_test_3.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

## NPV Knowledge Ratings {#npv-knowledge-materials-alignment-3}

A similar design to @long2018 [Study 1] was used to test whether this sample may
be overconfident in their understanding on NPV. Therefore, participants were
asked to rate their knowledge of NPV in various points in the study (see the
procedure in Section \@ref(procedure-alignment-3)).
Figure \@ref(fig:npv-knowledge-materials-alignment-3) shows an example of one
such display.

(ref:npv-knowledge-materials-alignment-3) Experiment 2 NPV knowledge rating task.

```{r npv-knowledge-materials-alignment-3, fig.cap = "(ref:npv-knowledge-materials-alignment-3)"}
file.path(
  materials_3,
  "npv_knowledge_1.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_contrast() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

\newpage
\newpage

## Variance Lecture {#variance-lecture-materials-alignment-3}

See below the slides for the variance lecture.

```{r, eval=knitr::is_html_output(), out.width='100%', out.height='1000px'}
file.path(
  materials_3,
  "variance_lecture.pdf"
) %>%
  include_graphics()
```

```{r, results='asis', eval=knitr::is_latex_output(), linewidth = 70}
## From https://ulyngs.github.io/oxforddown/customisations-and-extensions.html#embed-pdf
## \fbox added from https://tex.stackexchange.com/a/20641/233976

pdf_width <- 1.2

split_path <-
  file.path(
    materials_3,
    "variance_lecture_split/"
  )

slides <-
  split_path %>%
  list.files(full.names = TRUE)

slides %>%
  # for each PDF page, insert it nicely and
  # end with a page break
  paste0(
    "\\begin{figure} \\makebox[\\linewidth][c]{\\fbox{\\includegraphics[width=",
    pdf_width,
    "\\linewidth]{",
    .,
    "}}} \\caption{Variance lecture slide ",
    seq_along(slides),
    ".} \\end{figure}\n"
  ) %>%
  cat()
```

## Additional Analyses {#results-alignment-3-appendix}

### Ranking

A mixed factorial ANOVA was conducted to investigate the effects of NPV,
alignment, and numerical NPV reliability on participants’ project rankings.
Figure \@ref(fig:plot-alignment-3-ranking) shows these data. The alignment
$\times$ reliability level $\times$ NPV interaction was not
significant,
`r results_3$ranking$alignment_reliability_amount_npv_amount`.
However, the alignment $\times$ NPV interaction was significant,
`r results_3$ranking$alignment_npv_amount`; as well as the reliability
amount $\times$ NPV interaction,
`r results_3$ranking$reliability_amount_npv_amount`. As in the
allocation data, the linear NPV trend did not differ between reliability level
condition in neither the low alignment condition,
`r results_3$ranking$Linear_Low_high_Low`, nor the high alignment
condition, `r results_3$ranking$Linear_Low_high_High`. However,
averaging over reliability level, the linear NPV trend was higher in the low
alignment condition than in the high alignment condition,
`r results_3$ranking$Linear_Low_high`.

(ref:plot-alignment-3-ranking) Mean ranking.

```{r plot-alignment-3-ranking, fig.cap = "(ref:plot-alignment-3-ranking)"}
plot_3$ranking
```

### Confidence

A mixed factorial ANOVA was conducted to investigate the effects of NPV,
alignment, and numerical NPV reliability on participants’ confidence ratings.
Figure \@ref(fig:plot-alignment-3-confidence) shows these data. Only the main
effect of NPV was significant,
`r results_3$confidence$npv_amount`.

(ref:plot-alignment-3-confidence) Mean confidence.

```{r plot-alignment-3-confidence, fig.cap = "(ref:plot-alignment-3-confidence)"}
plot_3$confidence
```

### Variance Lecture

The allocation and ranking data show that participants were affected by the
similarity of options, but were not affected by variance information. After the
main task of this experiment, participants were shown a short lecture about the
importance of variance information when making allocation decisions. They were
then presented with half of their previous allocations and gave them an
opportunity to amend their allocations. It was hypothesised that participants
will be more sensitive to variance after the educational intervention.

A mixed factorial ANOVA was conducted to investigate the effects of phase on
participants' project allocations. As shown in
Figure \@ref(fig:plot-alignment-3-variance-lecture), the four-way interaction
was not significant,
`r results_3$variance_lecture$alignment_between_npv_amount_phase_reliability_amount`.
Further, the NPV $\times$ phase $\times$ reliability level interactions were not
significant for either the low alignment condition,
`r results_3$variance_lecture$Linear_Pre_post_Low_high_Low`; or the
high alignment conditions,
`r results_3$variance_lecture$Linear_Pre_post_Low_high_High`. In the
low alignment condition, the linear NPV trend (averaged over reliability level)
was significantly weaker after the lecture, compared with the linear NPV trend
before the lecture, `r results_3$variance_lecture$Linear_Pre_post_Low`.
However, this comparison was not significant in the high alignment condition,
`r results_3$variance_lecture$Linear_Pre_post_High`. These results
suggest that participants did not become better informed by NPV numerical
reliability after the variance lecture. There was, however, some reduction in
reliance on NPV overall when projects were dissimilar.

(ref:plot-alignment-3-variance-lecture) Mean allocation by NPV, reliability level, alignment, and phase.

```{r plot-alignment-3-variance-lecture, fig.height = 10, fig.width = 8, fig.pos = "!htbp", fig.cap = "(ref:plot-alignment-3-variance-lecture)"}
plot_3$variance_lecture
```

### NPV Knowledge

A repeated-measures ANOVA was conducted to investigate the effects of experiment
phase condition on participants’ NPV knowledge rating.
Figure \@ref(fig:plot-alignment-3-npv-knowledge) shows these data. The main
effect of phase was significant, `r results_3$npv_knowledge$rating`.
The post-explanation rating was significantly higher than the pre-explanation
rating,
`r results_3$npv_knowledge$X1_X2`. However, there were no significant
differences in rating between any of the later phases.

(ref:plot-alignment-3-npv-knowledge) Mean NPV knowledge rating.

```{r plot-alignment-3-npv-knowledge, fig.cap = "(ref:plot-alignment-3-npv-knowledge)"}
plot_3$npv_knowledge
```
