# Experiment 3

## Hypothesised Effects {#alignment-8-appendix}

Figure \@ref(fig:plot-simulation-alignment-8) shows the simulated hypothesised
effects for Experiment 3. These effects were constructed as a composite of
Experiment 1 data (without the no NPV condition) for the verbal reliability type
condition, and data from a pilot study [@dekel2021b, Appendix B.8] for the
numerical reliability type condition. Variance was removed to see the effects
clearer.

(ref:plot-simulation-alignment-8) Experiment 3 predicted data.

```{r plot-simulation-alignment-8, fig.cap = "(ref:plot-simulation-alignment-8)"}
alignment8::plot_simulation
```


## Power Analysis {#power-analysis-alignment-8}

A power analysis was conducted through simulation of the effects hypothesised in
Experiment 3 (and the simple effects implied by them). The simulated data used
the same regression coefficients as Experiment 2 for the explicit condition, no
effects for the implicit condition (as shown in
Figure \@ref(fig:plot-simulation-alignment-8)), and the intercept and residual
variance of Experiment 2. The null effects were analysed using the two one-sided
tests (TOST) procedure, or *equivalence* testing [@lakens2018], and setting the
smallest effect size of interest to the smallest difference that leads to a
significant equivalence between low and high implicit reliability for low
alignment in a pilot study [@dekel2021b, Appendix B.8].
Figure \@ref(fig:power-curve-alignment-8) shows the resulting power curve. The
analysis suggests a total sample size of `r alignment8::power$n_total`
(`r alignment8::power$n` $\cdot$ 4).

\newpage

\blandscape

(ref:power-curve-alignment-8) Alignment Experiment 3 power curve. Labels indicate lowest sample size above 80% power.

```{r power-curve-alignment-8, fig.width = 13, fig.height = 7, fig.cap = "(ref:power-curve-alignment-8)"}
alignment8::power$power_curve
```

\elandscape

\newpage

## Instructions {#instructions-materials-alignment-8-appendix}

Figures \@ref(fig:instructions-reliability-explicit-materials-alignment-8)
and \@ref(fig:instructions-reliability-implicit-materials-alignment-8) show the
instructions for the verbal and numerical reliability conditions, respectively.

(ref:instructions-reliability-explicit-materials-alignment-8) Experiment 3 verbal reliability instructions.

```{r instructions-reliability-explicit-materials-alignment-8, fig.cap = "(ref:instructions-reliability-explicit-materials-alignment-8)"}
file.path(
  materials_8,
  "instructions_reliability_type_explicit.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

(ref:instructions-reliability-implicit-materials-alignment-8) Experiment 3 numerical reliability instructions.

```{r instructions-reliability-implicit-materials-alignment-8, fig.cap = "(ref:instructions-reliability-implicit-materials-alignment-8)"}
file.path(
  materials_8,
  "instructions_reliability_type_implicit.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

## Interstitial Display {#interstitial-materials-alignment-8}

Figure \@ref(fig:interstitial-materials-alignment-8) shows an example of an
interstitial display.

(ref:interstitial-materials-alignment-8) An example of an interstitial display in Experiment 3.

```{r interstitial-materials-alignment-8, fig.cap = "(ref:interstitial-materials-alignment-8)"}
file.path(
  materials_8,
  "interstitial_1.png"
) %>%
  image_read() %>%
  image_trim() %>%
  image_border(color = "white", geometry = "5x5") %>%
  image_border(color = "black", geometry = "5x5")
```

## Additional Analyses {#results-alignment-8-allocation}

The three-way interaction (reliability level $\times$ NPV $\times$ reliability
type) in the high alignment condition was significant,
`r results_8$allocation$alignment_high_three_way`. The NPV $\times$
reliability type (averaging over reliability level) in the low alignment
condition was significant,
`r results_8$allocation$alignment_low_two_way`. The association
between allocation and NPV for those in the explicit low reliability
condition was significantly stronger for those in the low alignment condition,
than for those in the high alignment condition,
`r results_8$allocation$reliability_type_explicit_reliability_amount_low_alignment`.
The linear NPV trend for those in the low alignment condition was
significantly stronger for those in the explicit reliability condition, than for
those in the implicit reliability condition (averaging over reliability level),
`r results_8$allocation$alignment_low_reliability_type`. The linear
NPV trend for those in the implicit reliability condition was not
significantly "equivalent" between those in the low and high reliability
conditions for both those in the low alignment
`r results_8$allocation$alignment_low_reliability_type_implicit_reliability_amount_null`
and high alignment conditions
`r results_8$allocation$alignment_high_reliability_type_implicit_reliability_amount_null`.
However, this is likely to be because the "lowest effect size of interest"
estimate originated from an analysis used before data collection that was
different to the one that one used after data collection. Specifically, a
univariate linear model was originally used (treating NPV as a continuous
predictor), whereas the data were ultimately analysed using a multivariate
linear model (treating NPV as a repeated measures factor). In the numerical
reliability condition, a pilot experiment [@dekel2021b, Appendix B.8]
suggested that the linear NPV trend would be equivalent between those in the low
and high alignment conditions, averaged over reliability level. However, the
test of equivalence was not significant,
`r results_8$allocation$reliability_type_implicit_alignment_null`.
